%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Organizational Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Core Team Member Google Developer Student Club} % Job title
    {AISSMS COE} % Organisation
    {Pune, India} % Location
    {Sept 2020 - Sept 2022} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Led the Competitive Programming Team and organized multiple virtual and in-person events for freshmen and juniors.}
        \item {Conducted events focused on Git, Data Structures, Algorithms, and Competitive Programming, helping participants understand fundamental concepts and improve their coding skills.}
        \item {Contributed as a member of the Web Development Team to the \exthref{https://dsc-aissmscoe.web.app/}{DSC AISSMSCOE} official website.}
        \item {\textbf{Technical Skills:} Python (Algorithms, Data Structures), Tailwind CSS, Firebase, Git.}
        \item {\textbf{Soft Skills:} Leadership, Time Management, Communication, Logical Thinking.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Core Team Member Microsoft Student Club} % Job title
    {AISSMS COE} % Organisation
    {Pune, India} % Location
    {July 2021 - Sept 2022} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Built a university \exthref{https://github.com/PROxZIMA/TimetableScheduler}{Timetable Scheduler} model with a colleague, which uses a genetic algorithm and is portable for various scheduling scenarios, such as school timetables or employee timesheets.}
        \item {Designed the scheduler to be flexible for any case, with lower time complexity compared to existing models that were only useful in specific scenarios.}
        \item {Developed a \exthref{https://github.com/PROxZIMA/certificate-app/}{Certificate App} for easier certificate generation and distribution, which helped the college's Sports Department manage certificates for competitions and events.}
        \item {\textbf{Technical Skills:} Python with genetic algorithms, Django, HTML5, CSS3, JavaScript, CI \& CD, Git.}
        \item {\textbf{Soft Skills:} Teamwork, time management, communication, logical thinking.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
