%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\filbreak
\cvsection{Projects}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

    %---------------------------------------------------------
    \cventry
    {AISSMS COE} % Organisation
    {\exthref{https://proxzima.dev/DarkSpider/}{DarkSpider}} % Project
    {Pune, India} % Location
    {Aug 2022 - Feb 2023} % Date(s)
    {
        \begin{cvitems} % Description(s) of project
            \item {\exthref{http://www.isteonline.in/Datafiles/cms//Special\%20Issues//Special\%20issue\%20July\%202023.pdf\#\%5B\%7B\%22num\%22\%3A329\%2C\%22gen\%22\%3A0\%7D\%2C\%7B\%22name\%22\%3A\%22FitH\%22\%7D\%2C796\%5D}{Anatomy of the Dark Web’s Network Structure to Detect Illicit websites}}
            \item {Built a focused, multithreaded crawler that maps dark-net sites as a directed graph and applies PageRank to identify high-value nodes for further analysis.}
            \item {Implemented incremental crawling with content-based ranking, change detection, and URL expiration handling to keep the dataset current and reduce redundant fetches.}
            \item {Ensured operational safety through rate limiting, sandboxed execution, and systematized test harnesses, minimizing crawl impact and aligning with ethical research practices.}
        \end{cvitems}
    }

    %---------------------------------------------------------
    \cventry
    {AISSMS COE} % Organisation
    {\exthref{https://github.com/PROxZIMA/TimetableScheduler}{Timetable Scheduler}} % Project
    {Pune, India} % Location
    {Sept 2021 - Jan 2022} % Date(s)
    {
        \begin{cvitems} % Description(s) of project
            \item {Developed an intelligent timetable generator for university scheduling using a Genetic Algorithm, automating the creation of conflict-free timetables.}
            \item {Designed and implemented logic to satisfy both hard constraints (such as no overlapping classes and room availability) and soft constraints (such as preferred time slots and faculty preferences) to optimize scheduling efficiency.}
            \item {Built the system using Python and Django, leveraging Genetic Algorithms for iterative improvement and solution convergence.}
            \item {Enhanced teamwork and project delivery through effective time management, collaborative problem-solving, and clear presentations of technical concepts.}
        \end{cvitems}
    }

    %---------------------------------------------------------
    \cventry
    {Personal Project} % Organisation
    {\exthref{https://github.com/PROxZIMA/Museum-Gallery}{Museum Gallery}} % Project
    {Pune, India} % Location
    {May 2020 - Aug 2020} % Date(s)
    {
        \begin{cvitems} % Description(s) of project
            \item {Created a virtual reality museum application enabling users to explore museum galleries remotely, enhancing accessibility and user engagement.}
            \item {Developed the application for Android using Java and integrated Google VR SDK to deliver immersive 3D experiences.}
        \end{cvitems}
    }

    %---------------------------------------------------------
    \cventry
    {Personal Project} % Organisation
    {\exthref{https://github.com/PROxZIMA/Twitter-Sentiment-Analysis}{Twitter Sentiment Analysis}} % Project
    {Pune, India} % Location
    {Apr 2022 - May 2022} % Date(s)
    {
        \begin{cvitems} % Description(s) of project
            \item {Implemented sentiment analysis on Twitter data using vaderSentiment, CountVectorizer, and KMeans clustering to classify and visualize public opinion trends.}
            \item {Processed and cleaned tweet texts by removing stop words, tokenizing, stemming, and lemmatizing to improve model accuracy and reliability.}
            \item {Utilized Python libraries including Pandas, NumPy, seaborn, and scikit-learn for data manipulation, analysis, and visualization.}
        \end{cvitems}
    }

    % %---------------------------------------------------------
    % \cventry
    % {Personal Project} % Organisation
    % {\exthref{https://proxzima.dev/}{proxzima.dev}} % Project
    % {Pune, India} % Location
    % {May 2022 - Current} % Date(s)
    % {
    %     \begin{cvitems} % Description(s) of project
    %         \item {Developed a highly customizable, minimalistic, terminal-styled personal website using Next.js, designed for ease of use and rapid deployment.}
    %         \item {Implemented features such as dynamic content rendering, responsive design, and shell-inspired navigation to enhance user experience.}
    %         \item {Utilized TypeScript, React.js, Next.js, HTML5, CSS3, JavaScript, and Shell Scripting to build and maintain the platform.}
    %     \end{cvitems}
    % }

    %---------------------------------------------------------
\end{cventries}
